### 2009-11-27 doc/tech_doc/client/job_description_mapping.tex
Updating job description mapping document.

\subsection{JobIdentification}
\subsubsection{JobName}
\begin{table}[h]
\begin{inouttabular}
XRSL & jobname & jobname\\
JDL & No matching attribute & Not mapped\\
JSDL & JobIdentification/JobName & JobIdentification/JobName\\
ARC-JSDL &  & \\
\end{inouttabular}
\end{table}

@@

\subsection{Application}
\subsubsection{Executable}
\begin{inouttabular}
XRSL & executable, arguments & executable, arguments\\
JDL & Executable, Arguments & Executable, Arguments\\
\multirow{2}{*}{Posix-JSDL} & Application/POSIXApplication/Executable, & Application/POSIXApplication/Executable,\\
&  Application/POSIXApplication/Arguments & Application/POSIXApplication/Arguments\\
\multirow{2}{*}{HPCP-JSDL} & Application/HPCProfileApplication/Executable, & Application/HPCProfileApplication/Executable,\\
&  Application/HPCProfileApplication/Arguments & Application/HPCProfileApplication/Arguments\\
\multirow{2}{*}{ARC-JSDL} & Application/Executable/Path, & Application/Executable/Path,\\
 & Application/Executable/Argument & Application/Executable/Argument\\
\end{inouttabular}
The Executable data member is a composite structure of a string and a
list of strings, where the string holds the executable and the list
holding the arguments.

\subsubsection{Input}
\begin{inouttabular}
XRSL & stdin & stdin, inputFiles\\
JDL & StdInput & StdInput, InputSandbox\\
Posix-JSDL & Application/POSIXApplication/Input & Application/POSIXApplication/Input\\
HPCP-JSDL & Application/HPCProfileApplication/Input & Application/HPCProfileApplication/Input\\
ARC-JSDL & Application/Input & \\
\end{inouttabular}
If the Input data member does not exist in the file list, it will be
added to it.

\subsubsection{Output}
\begin{inouttabular}
XRSL & stdout & stdout, outputFiles\\
JDL & StdOutput & StdOutput, OutputSandbox, OutputSandboxDestURI\\
Posix-JSDL & Application/POSIXApplication/Output & \\
HPCP-JSDL & Application/HPCProfileApplication/Output & \\
ARC-JSDL & Application/Output & \\
\end{inouttabular}
If the Output data member does not exist in the File
list, it will be added to it.

\subsubsection{Error}
\begin{inouttabular}
XRSL & stderr & stderr, outputFiles\\
JDL & StdError & StdError, OutputSandbox, OutputSandboxDestURI\\
Posix-JSDL & Application/POSIXApplication/Error &\\
HPCP-JSDL & Application/HPCProfileApplication/Error &\\
ARC-JSDL & Application/Error & \\
\end{inouttabular}
If the Error data member does not exist in the File list, it will be
added to it.

\subsubsection{Join}
\begin{inouttabular}
XRSL & join & Not mapped\todo{}\\
ARC-JSDL & Application/Join & Application/Join\\
\end{inouttabular}

\subsubsection{Environment}
\subsubsubsection{Name}
\begin{inouttabular}
XRSL & environment* & environment*\\
JDL & Environment** & Environment**\\
Posix-JSDL & Application/POSIXApplication/Environment.name & Application/POSIXApplication/Environment.name\\
HPCP-JSDL & Application/HPCProfileApplication/Environment.name & Application/HPCProfileApplication/Environment.name\\
ARC-JSDL & Application/Environment/Name & ~\\
\end{inouttabular}
The XRSL attribute environment is a list of
pairs. The first element of each pair is mapped to the Name data member.
The JDL attribute Environment is a list of equalities.

\subsubsubsection{Value}
\begin{inouttabular}
XRSL & environment* & environment*\\
JDL & Environment** & Environment**\\
JSDL & No matching attribute & Not mapped\\
Posix-JSDL & Application/POSIXApplication/Environment & Application/POSIXApplication/Environment\\
HPCP-JSDL & Application/HPCProfileApplication/Environment & Applicaion/HPCProfileApplication/Environment\\
ARC-JSDL & Application/Environment/Value & ~\\
\end{inouttabular}

@@

\subsubsection{LogDir}
\begin{inouttabular}
XRSL & gmlog & gmlog outputFiles\\
ARC-JSDL & Application/LogDir & Application/LogDir\\
\end{inouttabular}

@@

\subsubsection{StartOnHold}
\begin{inouttabular}
\end{inouttabular}

@@

\subsubsection{Platform}
\begin{inouttabular}
XRSL & architecture & architecture\\
JSDL & Resources/CPUAchitecture/CPUArchitectureName & ~\\
ARC-JSDL & Resources/Platform &~\\
\end{inouttabular}

\subsubsection{NetworkInfo}
\begin{inouttabular}
JSDL & Resources/IndividualNetworkBandwidth &\\
ARC-JSDL & Resources/NetworkInfo &\\
\end{inouttabular}

\subsubsection{NodeAccess}
\begin{inouttabular}
XRSL & nodeAccess & nodeAccess\\
ARC-JSDL & Resources/NodeAccess & ~\\
\end{inouttabular}

\subsubsection{IndividualPhysicalMemory}
\begin{inouttabular}
XRSL & memory & memory\\
Posix-JSDL & Application/POSIXApplication/MemoryLimit &\\
ARC-JSDL & Resources/IndividualPhysicalMemory &\\
\end{inouttabular}

\subsubsection{IndividualVirtualMemory}
\begin{inouttabular}
Posix-JSDL & Application/POSIXApplication/VirtualMemoryLimit &\\
ARC-JSDL & Resources/IndividualVirtualMemory &\\
\end{inouttabular}

\subsubsection{DiskSpaceRequirement}
\subsubsubsection{DiskSpace}
\begin{inouttabular}
XRSL & disk & disk\\
JSDL & Application/FileSystem/DiskSpace &\\
ARC-JSDL & Resources/DiskSpaceRequirement/DiskSpace &\\
\end{inouttabular}

@@

\subsubsection{SessionAccessMode}
\begin{inouttabular}
\end{inouttabular}

\subsubsection{IndividualCPUTime}
\begin{inouttabular}
JSDL & Resources/IndividualCPUTime* &\\
ARC-JSDL & Resources/IndividualCPUTime &\\
\end{inouttabular}
* The JSDL element is mapped to the Range part of
IndividualCPUTime.

\subsubsection{TotalCPUTime}
\begin{inouttabular}
XRSL & cpuTime & cpuTime\\
JSDL & Resources/TotalCPUTime* &\\
Posix-JSDL & Application/POSIXApplication/CPUTimeLimit* &\\
ARC-JSDL & Resources/TotalCPUTime &\\
\end{inouttabular}
* The JSDL and POSIX-JSDL elements is mapped to the
Range part of TotalCPUTime.

\subsubsection{IndividualWallTime}
\begin{inouttabular}
ARC-JSDL & Resources/IndividualWallTime &\\
\end{inouttabular}

\subsubsection{TotalWallTime}
\begin{inouttabular}
XRSL & wallTime & wallTime\\
Posix-JSDL & Application/POSIXApplication/WallTimeLimit &\\
ARC-JSDL & Resources/TotalWallTime &\\
\end{inouttabular}

\subsubsection{Homogeneous}
\begin{inouttabular}
\end{inouttabular}

\subsubsection{Benchmark}
\subsubsubsection{Type}
\begin{inouttabular}
\end{inouttabular}

\subsubsubsection{Value}
\begin{inouttabular}
\end{inouttabular}

@@

\subsubsection{SlotRequirement}
\subsubsubsection{NumberOfSlots}
\begin{inouttabular}
Posix-JSDL & Application/POSIXApplication/ProcessCountLimit &\\
ARC-JSDL & Resources/SlotRequirement/NumberOfSlots &\\
\end{inouttabular}

\subsubsubsection{ProcessPerHost}
\begin{inouttabular}
XRSL & count & count\\
JSDL & Resources/TotalCPUCount & \\
ARC-JSDL & Resources/SlotRequirement/ProcessPerHost &\\
\end{inouttabular}

\subsubsubsection{ThreadsPerProcesses}
\begin{inouttabular}
Posix-JSDL & Application/POSIXApplication/ThreadCountLimit &\\
ARC-JSDL & Resources/SlotRequirement/ThreadsPerProcesses &\\
\end{inouttabular}

\subsubsubsection{SPMDVariation}
\begin{inouttabular}
ARC-JSDL & Resources/SlotRequirement/SPMDVariation &\\
\end{inouttabular}

\subsubsection{CandidateTarget}
\subsubsubsection{EndPointURL}
\begin{inouttabular}
XRSL & cluster & Not mapped\\
JSDL & Resources/CandidateHosts/HostName &\\
ARC-JSDL & Resources/CandidateTarget/EndPointURL & Resources/CandidateTarget/EndPointURL\\
\end{inouttabular}

@@

\subsection{DataStaging}
\subsubsection{File}
\subsubsubsection{Name}
\begin{inouttabular}
XRSL & &\\
JDL & &\\
JSDL & &\\
Posix-JSDL & &\\
HPCP-JSDL & &\\
ARC-JSDL & &\\
\end{inouttabular}

\subsubsubsection{Source}
\subsubsubsubsection{URL}
\begin{inouttabular}
XRSL & &\\
JDL & &\\
JSDL & &\\
Posix-JSDL & &\\
HPCP-JSDL & &\\
ARC-JSDL & &\\
\end{inouttabular}

\subsubsubsubsection{Threads}
\begin{inouttabular}
XRSL & &\\
JDL & &\\
JSDL & &\\
Posix-JSDL & &\\
HPCP-JSDL & &\\
ARC-JSDL & &\\
\end{inouttabular}

\subsubsubsubsection{DataIndexingService}
\begin{inouttabular}
XRSL & &\\
JDL & &\\
JSDL & &\\
Posix-JSDL & &\\
HPCP-JSDL & &\\
ARC-JSDL & &\\
\end{inouttabular}

\subsubsubsection{Target}
\subsubsubsubsection{URL}
\begin{inouttabular}
XRSL & &\\
JDL & &\\
JSDL & &\\
Posix-JSDL & &\\
HPCP-JSDL & &\\
ARC-JSDL & &\\
\end{inouttabular}

\subsubsubsubsection{Threads}
\begin{inouttabular}
XRSL & &\\
JDL & &\\
JSDL & &\\
Posix-JSDL & &\\
HPCP-JSDL & &\\
ARC-JSDL & &\\
\end{inouttabular}

\subsubsubsubsection{Mandatory}
\begin{inouttabular}
XRSL & &\\
JDL & &\\
JSDL & &\\
Posix-JSDL & &\\
HPCP-JSDL & &\\
ARC-JSDL & &\\
\end{inouttabular}

\subsubsubsubsection{DataIndexingService}
\begin{inouttabular}
XRSL & &\\
JDL & &\\
JSDL & &\\
Posix-JSDL & &\\
HPCP-JSDL & &\\
ARC-JSDL & &\\
\end{inouttabular}

\subsubsubsubsection{NeededReplica}
\begin{inouttabular}
XRSL & &\\
JDL & &\\
JSDL & &\\
Posix-JSDL & &\\
HPCP-JSDL & &\\
ARC-JSDL & &\\
\end{inouttabular}

\subsubsubsection{KeepData}
\begin{inouttabular}
XRSL & &\\
JDL & &\\
JSDL & &\\
Posix-JSDL & &\\
HPCP-JSDL & &\\
ARC-JSDL & &\\
\end{inouttabular}

\subsubsubsection{IsExecutable}
\begin{inouttabular}
XRSL & &\\
JDL & &\\
JSDL & &\\
Posix-JSDL & &\\
HPCP-JSDL & &\\
ARC-JSDL & &\\
\end{inouttabular}

\subsubsubsection{DownloadToCache}
\begin{inouttabular}
XRSL & &\\
JDL & &\\
JSDL & &\\
Posix-JSDL & &\\
HPCP-JSDL & &\\
ARC-JSDL & &\\
\end{inouttabular}

\subsubsection{Directory}

\subsection{JobMetaData}
\subsubsection{Author}
\begin{inouttabular}
XRSL & &\\
JDL & &\\
JSDL & &\\
Posix-JSDL & &\\
HPCP-JSDL & &\\
ARC-JSDL & &\\
\end{inouttabular}

\subsubsection{DocumentExpiration}
\begin{inouttabular}
XRSL & &\\
JDL & &\\
JSDL & &\\
Posix-JSDL & &\\
HPCP-JSDL & &\\
ARC-JSDL & &\\
\end{inouttabular}

\subsubsection{Rank}
\begin{inouttabular}
XRSL & &\\
JDL & &\\
JSDL & &\\
Posix-JSDL & &\\
HPCP-JSDL & &\\
ARC-JSDL & &\\
\end{inouttabular}

\subsubsection{FuzzyRank}
\begin{inouttabular}
XRSL & ~ & ~\\
JDL & ~ & ~\\
JSDL & ~ & ~\\
Posix-JSDL & ~ & ~\\
HPCP-JSDL & ~ & ~\\
ARC-JSDL & ~ & ~\\
\end{inouttabular}

\section{XRSL mapping}
\begin{center}
\rowcolors{3}{tablerowcolor}{}
\begin{tabularx}{400pt}{CTC}
\toprule
\NST{XRSL input} & \NST{Internal representaion} & \NST{XRSL output}\\
\midrule
\defineheadfoot
executable & Application.Executable.Name & executable\\
arguments & Application.Executable.Arguments & arguments\\
inputFiles& DataStaging.File.Name,\linebreak DataStaging.File.Source & inputFiles\\
executables & DataStaging.File.IsExecutable & executables\\
cache & \TODO & \TODO \\
outputFiles & DataStaging.File.Name,\linebreak DataStaging.File.Target & outputFiles \\
cpuTime & Resources.TotalCPUTime & cpuTime\\
wallTime & Resources.TotalWallTime & wallTime\\
gridTime & Resources.TotalCPUTime & \NM \\
benchmarks & Resources.TotalCPUTime & \NM \\
memory & Resources.IndividualPhysicalMemory & memory\\
disk & Resources.DiskSpaceRequirement.DiskSpace & disk\\
runTimeEnvironment & Resources.RunTimeEnvironment & runTimeEnvironment\\
middleware & Resources.CEType & middleware\\
opsys & Resources.OperatingSystem & opsys\\
stdin & Application.Input & stdin\\
stdout & Application.Output & stdout, outputFiles\\
stderr & Application.Error & stderr, outputFiles\\
join & Application.Join & \NM\\
gmlog & Application.LogDir & gmlog\\
jobName & Identification.JobName & jobName\\
ftpThreads & DataStaging.File.Source.Threads,\linebreak DataStaging.File.Target.Threads & \NM\\
acl & Application.AccessControl & acl\\
cluster & Resources.CandidateTarget.EndPointURL & \NM\\
queue & Resources.CandidateTarget.QueueName & queue\\
startTime & Application.ProcessingStartTime & \NM\\
lifeTime & Resources.SessionLifeTime & lifeTime\\
notify & Application.Notification & notify\\
replicaCollection & DataStaging.File.DataIndexingService & \NM\\
rerun & Application.Rerun & rerun\\
architecture & Resources.Platform & architecture\\
nodeAccess & Resources.NodeAccess & \NM\\
dryRun & \NM & \NM\\
rsl\_substitution & \NST{Processed internally by the parser} & \NM\\
environment & Application.Environment & environment\\
count & Resources.SlotRequirement.ProcessPerHost & count\\
jobreport & Application.RemoteLogging & jobreport\\
credentialserver & Application.CredentialService & credentialserver\\
\end{tabularx}
\end{center}

>>>>

\subsection{JobIdentification}
\subsubsection{JobName}
\begin{table}[h]
\begin{inouttabular}
XRSL & jobname & jobname\\
JSDL & JobIdentification/JobName & JobIdentification/JobName\\
ARC-JSDL & JobIdentification/JobName & JobIdentification/JobName \\
\end{inouttabular}
\end{table}

@@

\subsection{Application}
\subsubsection{Executable}
\begin{inouttabular}
XRSL & executable, arguments & executable, arguments\\
JDL & Executable, Arguments & Executable, Arguments\\
\multirow{2}{*}{Posix-JSDL} & Application/POSIXApplication/Executable, & Application/POSIXApplication/Executable,\\
&  Application/POSIXApplication/Arguments & Application/POSIXApplication/Arguments\\
\multirow{2}{*}{HPCP-JSDL} & Application/HPCProfileApplication/Executable, & Application/HPCProfileApplication/Executable,\\
&  Application/HPCProfileApplication/Arguments & Application/HPCProfileApplication/Arguments\\
\end{inouttabular}
The Executable data member is a composite structure of a string and a
list of strings, where the string holds the executable and the list
holding the arguments.

\subsubsection{Input}
\begin{inouttabular}
XRSL & stdin & stdin, inputFiles\\
JDL & StdInput & StdInput, InputSandbox\\
Posix-JSDL & Application/POSIXApplication/Input & Application/POSIXApplication/Input\\
HPCP-JSDL & Application/HPCProfileApplication/Input & Application/HPCProfileApplication/Input\\
\end{inouttabular}
If the Input data member does not exist in the file list, it will be
added to it.

\subsubsection{Output}
\begin{inouttabular}
XRSL & stdout & stdout, outputFiles\\
JDL & StdOutput & StdOutput, OutputSandbox, OutputSandboxDestURI\\
Posix-JSDL & Application/POSIXApplication/Output & Application/POSIXApplication/Output\\
HPCP-JSDL & Application/HPCProfileApplication/Output & Application/HPCProfileApplication/Output\\
\end{inouttabular}
If the Output data member does not exist in the File
list, it will be added to it.

\subsubsection{Error}
\begin{inouttabular}
XRSL & stderr & stderr, outputFiles\\
JDL & StdError & StdError, OutputSandbox, OutputSandboxDestURI\\
Posix-JSDL & Application/POSIXApplication/Error & Application/POSIXApplication/Error\\
HPCP-JSDL & Application/HPCProfileApplication/Error & Application/HPCProfileApplication/Error\\
\end{inouttabular}
If the Error data member does not exist in the File list, it will be
added to it.

\subsubsection{Join}
\begin{inouttabular}
XRSL & join & \NM\\
ARC-JSDL & Application/Join & Application/Join\\
\end{inouttabular}

\subsubsection{Environment}
\subsubsubsection{Name}
\begin{inouttabular}
XRSL & environment* & environment*\\
JDL & Environment** & Environment**\\
Posix-JSDL & Application/POSIXApplication/Environment.name & Application/POSIXApplication/Environment.name\\
HPCP-JSDL & Application/HPCProfileApplication/Environment.name & Application/HPCProfileApplication/Environment.name\\
\end{inouttabular}
The XRSL attribute environment is a list of
pairs. The first element of each pair is mapped to the Name data member.
The JDL attribute Environment is a list of equalities.

\subsubsubsection{Value}
\begin{inouttabular}
XRSL & environment* & environment*\\
JDL & Environment** & Environment**\\
JSDL & No matching attribute & Not mapped\\
Posix-JSDL & Application/POSIXApplication/Environment & Application/POSIXApplication/Environment\\
HPCP-JSDL & Application/HPCProfileApplication/Environment & Applicaion/HPCProfileApplication/Environment\\
\end{inouttabular}

@@

\subsubsection{LogDir}
\begin{inouttabular}
XRSL & gmlog & gmlog, outputFiles\\
ARC-JSDL & Application/LogDir & Application/LogDir\\
\end{inouttabular}

@@

@@

\subsubsection{Platform}
\begin{inouttabular}
XRSL & architecture & architecture\\
JSDL & Resources/CPUAchitecture/CPUArchitectureName & Resources/CPUAchitecture/CPUArchitectureName\\
ARC-JSDL & Resources/Platform & Resources/Platform\\
\end{inouttabular}

\subsubsection{NetworkInfo}
\begin{inouttabular}
JSDL & Resources/IndividualNetworkBandwidth & Resources/IndividualNetworkBandwidth \\
ARC-JSDL & Resources/NetworkInfo & \NM\\
\end{inouttabular}

\subsubsection{NodeAccess}
\begin{inouttabular}
XRSL & nodeAccess & nodeAccess\\
ARC-JSDL & Resources/NodeAccess & Resources/NodeAccess\\
\end{inouttabular}

\subsubsection{IndividualPhysicalMemory}
\begin{inouttabular}
XRSL & memory & memory\\
JSDL & Resources/IndividualPhysicalMemory & Resources/IndividualPhysicalMemory\\
Posix-JSDL & Application/POSIXApplication/MemoryLimit & Application/POSIXApplication/MemoryLimit\\
ARC-JSDL & Resources/IndividualPhysicalMemory & Resources/IndividualPhysicalMemory\\
\end{inouttabular}

\subsubsection{IndividualVirtualMemory}
\begin{inouttabular}
JSDL & Resources/IndividualVirtualMemory & Resources/IndividualVirtualMemory\\
Posix-JSDL & Application/POSIXApplication/VirtualMemoryLimit & Application/POSIXApplication/VirtualMemoryLimit\\
ARC-JSDL & Resources/IndividualVirtualMemory & Resources/IndividualVirtualMemory\\
\end{inouttabular}

\subsubsection{DiskSpaceRequirement}
\subsubsubsection{DiskSpace}
\begin{inouttabular}
XRSL & disk & disk\\
JSDL & Resources/FileSystem/DiskSpace & Resources/FileSystem/DiskSpace\\
ARC-JSDL & Resources/DiskSpaceRequirement/DiskSpace & Resources/DiskSpaceRequirement/DiskSpace\\
\end{inouttabular}

@@

\subsubsection{IndividualCPUTime}
\begin{inouttabular}
JSDL & Resources/IndividualCPUTime* & Resources/IndividualCPUTime\\
ARC-JSDL & Resources/IndividualCPUTime & Resources/IndividualCPUTime\\
\end{inouttabular}
* The JSDL element is mapped to the Range part of
IndividualCPUTime.

\subsubsection{TotalCPUTime}
\begin{inouttabular}
XRSL & cpuTime, gridtime, benchmark & cpuTime\\
JSDL & Resources/TotalCPUTime* & Resources/TotalCPUTime\\
Posix-JSDL & Application/POSIXApplication/CPUTimeLimit* & Application/POSIXApplication/CPUTimeLimit\\
ARC-JSDL & Resources/TotalCPUTime & Resources/TotalCPUTime\\
\end{inouttabular}
The \texttt{XRSL} attribute \texttt{cputime} is mapped to the
\texttt{Range} part of \texttt{TotalCPUTime}, where as for the
\texttt{gridtime} attibute the pair ("ARC-gridtime", 1800) will
be added to the benchmark part.
The JSDL and POSIX-JSDL elements is mapped to the Range part of
TotalCPUTime.

\subsubsection{IndividualWallTime}
\begin{inouttabular}
ARC-JSDL & Resources/IndividualWallTime & Resources/IndividualWallTime\\
\end{inouttabular}

\subsubsection{TotalWallTime}
\begin{inouttabular}
XRSL & wallTime & wallTime\\
Posix-JSDL & Application/POSIXApplication/WallTimeLimit & Application/POSIXApplication/WallTimeLimit\\
ARC-JSDL & Resources/TotalWallTime & Resources/TotalWallTime\\
\end{inouttabular}

@@

\subsubsection{SlotRequirement}
\subsubsubsection{NumberOfSlots}
\begin{inouttabular}
Posix-JSDL & Application/POSIXApplication/ProcessCountLimit & Application/POSIXApplication/ProcessCountLimit\\
ARC-JSDL & Resources/SlotRequirement/NumberOfSlots & Resources/SlotRequirement/NumberOfSlots\\
\end{inouttabular}

\subsubsubsection{ProcessPerHost}
\begin{inouttabular}
XRSL & count & count\\
JSDL & Resources/TotalCPUCount & Resources/TotalCPUCount\\
ARC-JSDL & Resources/SlotRequirement/ProcessPerHost & Resources/SlotRequirement/ProcessPerHost\\
\end{inouttabular}

\subsubsubsection{ThreadsPerProcesses}
\begin{inouttabular}
Posix-JSDL & Application/POSIXApplication/ThreadCountLimit & Application/POSIXApplication/ThreadCountLimit\\
ARC-JSDL & Resources/SlotRequirement/ThreadsPerProcesses & Resources/SlotRequirement/ThreadsPerProcesses\\
\end{inouttabular}

\subsubsubsection{SPMDVariation}
\begin{inouttabular}
ARC-JSDL & Resources/SlotRequirement/SPMDVariation & Resources/SlotRequirement/SPMDVariation\\
\end{inouttabular}

\subsubsection{CandidateTarget}
\subsubsubsection{EndPointURL}
\begin{inouttabular}
XRSL & cluster & \NM\\
JSDL & Resources/CandidateHosts/HostName & \NM\\
ARC-JSDL & Resources/CandidateTarget/EndPointURL & Resources/CandidateTarget/EndPointURL\\
\end{inouttabular}

@@

\subsection{DataStaging}
\subsubsection{File}
\subsubsubsection{Name}
\begin{inouttabular}
XRSL & inputFiles, outputFiles & inputFiles, outputFiles\\
JDL & InputSandbox, OutputSandbox & InputSandbox, OutputSandbox\\
JSDL & DataStaging/File/FileName & DataStaging/File/FileName\\
\end{inouttabular}

\subsubsubsection{Source}
\subsubsubsubsection{URI}
\begin{inouttabular}
XRSL & inputFiles & inputFiles\\
JDL & InputSandbox, InputSandboxURI & InputSandbox, InputSandboxURI\\
JSDL & DataStaging/File/Source/URI & DataStaging/File/Source/URI\\
\end{inouttabular}

\subsubsubsubsection{Threads}
\begin{inouttabular}
XRSL & ftpThreads & ftpThreads\\
%~ ARC-JSDL & &\\
\end{inouttabular}

%~ \subsubsubsubsection{DataIndexingService}
%~ \begin{inouttabular}
%~ XRSL & &\\
%~ JDL & &\\
%~ JSDL & &\\
%~ Posix-JSDL & &\\
%~ HPCP-JSDL & &\\
%~ ARC-JSDL & &\\
%~ \end{inouttabular}

\subsubsubsection{Target}
\subsubsubsubsection{URI}
\begin{inouttabular}
XRSL & outputFiles & outputFiles\\
JDL & OutputSandbox, OutputSandboxDestURI & OutputSandbox, OutputSandboxDestURI\\
JSDL & DataStaging/File/Target/URI & DataStaging/File/Target/URI\\
\end{inouttabular}

\subsubsubsubsection{Threads}
\begin{inouttabular}
XRSL & ftpThreads &ftpThreads\\
%~ ARC-JSDL & &\\
\end{inouttabular}

%~ \subsubsubsubsection{Mandatory}
%~ \begin{inouttabular}
%~ XRSL & &\\
%~ JDL & &\\
%~ JSDL & &\\
%~ Posix-JSDL & &\\
%~ HPCP-JSDL & &\\
%~ ARC-JSDL & &\\
%~ \end{inouttabular}

%~ \subsubsubsubsection{DataIndexingService}
%~ \begin{inouttabular}
%~ XRSL & &\\
%~ JDL & &\\
%~ JSDL & &\\
%~ Posix-JSDL & &\\
%~ HPCP-JSDL & &\\
%~ ARC-JSDL & &\\
%~ \end{inouttabular}

%~ \subsubsubsubsection{NeededReplica}
%~ \begin{inouttabular}
%~ XRSL & &\\
%~ JDL & &\\
%~ JSDL & &\\
%~ Posix-JSDL & &\\
%~ HPCP-JSDL & &\\
%~ ARC-JSDL & &\\
%~ \end{inouttabular}

\subsubsubsection{KeepData}
\begin{inouttabular}
JDL & OutputSandboxDestURI & OutputSandboxDestURI\\
JSDL & DataStaging/File/DeleteOnTermination & DataStaging/File/DeleteOnTermination\\
\end{inouttabular}

\subsubsubsection{IsExecutable}
\begin{inouttabular}
XRSL & executables & executables\\
ARC-JSDL & DataStaging/File/IsExecutable & DataStaging/File/IsExecutable\\
\end{inouttabular}

\subsubsubsection{DownloadToCache}
\begin{inouttabular}
XRSL & \todo{} & \todo{}\\
ARC-JSDL & DataStaging/File/DownloadToCache & DataStaging/File/DownloadToCache\\
\end{inouttabular}

%~ \subsubsection{Directory}

\subsection{JobMetaData}
%~ \subsubsection{Author}
%~ \begin{inouttabular}
%~ XRSL & &\\
%~ JDL & &\\
%~ JSDL & &\\
%~ Posix-JSDL & &\\
%~ HPCP-JSDL & &\\
%~ ARC-JSDL & &\\
%~ \end{inouttabular}
%~
%~ \subsubsection{DocumentExpiration}
%~ \begin{inouttabular}
%~ XRSL & &\\
%~ JDL & &\\
%~ JSDL & &\\
%~ Posix-JSDL & &\\
%~ HPCP-JSDL & &\\
%~ ARC-JSDL & &\\
%~ \end{inouttabular}

\subsubsection{Rank}
\begin{inouttabular}
JDL & Rank & Rank\\
%~ ARC-JSDL & &\\
\end{inouttabular}

\subsubsection{FuzzyRank}
\begin{inouttabular}
JDL & FuzzyRank & FuzzyRank\\
%~ ARC-JSDL & & \\
\end{inouttabular}

\section{XRSL mapping}
\begin{center}
\rowcolors{3}{tablerowcolor}{}
\begin{tabularx}{400pt}{CTC}
\toprule
\NST{XRSL input} & \NST{Internal representaion} & \NST{XRSL output}\\
\midrule
\defineheadfoot
executable & Application.Executable.Name & executable\\
arguments & Application.Executable.Arguments & arguments\\
inputFiles& DataStaging.File.Name,\linebreak DataStaging.File.Source & inputFiles\\
executables & DataStaging.File.IsExecutable & executables\\
cache & \TODO & \TODO \\
outputFiles & DataStaging.File.Name,\linebreak DataStaging.File.Target & outputFiles \\
cpuTime & Resources.TotalCPUTime & cpuTime\\
wallTime & Resources.TotalWallTime & wallTime\\
gridTime & Resources.TotalCPUTime & \NM \\
benchmarks & Resources.TotalCPUTime & \NM \\
memory & Resources.IndividualPhysicalMemory & memory\\
disk & Resources.DiskSpaceRequirement.DiskSpace & disk\\
runTimeEnvironment & Resources.RunTimeEnvironment & runTimeEnvironment\\
middleware & Resources.CEType & middleware\\
opsys & Resources.OperatingSystem & opsys\\
stdin & Application.Input & stdin\\
stdout & Application.Output & stdout, outputFiles\\
stderr & Application.Error & stderr, outputFiles\\
join & Application.Join & \NM\\
gmlog & Application.LogDir & gmlog\\
jobName & Identification.JobName & jobName\\
ftpThreads & DataStaging.File.Source.Threads,\linebreak DataStaging.File.Target.Threads & \NM\\
acl & Application.AccessControl & acl\\
cluster & Resources.CandidateTarget.EndPointURL & \NM\\
queue & Resources.CandidateTarget.QueueName & queue\\
startTime & Application.ProcessingStartTime & \NM\\
lifeTime & Resources.SessionLifeTime & lifeTime\\
notify & Application.Notification & notify\\
replicaCollection & \NM & \NM\\
rerun & Application.Rerun & rerun\\
architecture & Resources.Platform & architecture\\
nodeAccess & Resources.NodeAccess & \NM\\
dryRun & \NM & \NM\\
rsl\_substitution & \NST{Processed internally by the parser} & \NM\\
environment & Application.Environment & environment\\
count & Resources.SlotRequirement.ProcessPerHost & count\\
jobreport & Application.RemoteLogging & jobreport\\
credentialserver & Application.CredentialService & credentialserver\\
\end{tabularx}
\end{center}

\section{JDL mapping}
\begin{center}
\rowcolors{3}{}{tablerowcolor}
\begin{tabularx}{\textwidth}{CTT}
\toprule
\rowcolor{white}
\NST{JDL input} & \NST{Internal representaion} & \NST{JDL output}\\
\midrule
\defineheadfoot
JobType & \NM & \NM\\
Executable & Application.Executable.Name & Executable, InputSandbox\\
Arguments & Application.Executable.Arguments & Arguments\\
StdInput & Application.Input & StdInput,\linebreak InputSandbox\\
StdOutput & Application.Output & StdOutput,\linebreak OutputSandbox,\linebreak OutputSandboxDestURI\\
StdError & Application.Error & StdError,\linebreak OutputSandbox,\linebreak OutputSandboxDestURI\\
InputSandbox & DataStaging.File.Name,\linebreak DataStaging.File.Source & InputSandbox\\
InputSandboxBaseURI & DataStaging.File.Source.URI & InputSandbox\\
OutputSandbox & DataStaging.File.Name,\linebreak DataStaging.File.Target.URI & OutputSandbox,\linebreak OutputSandboxDestURI\\
OutputSandboxDestURI & DataStaging.File.Target,\linebreak DataStaging.File.KeepData & OutputSandbox,\linebreak OutputSandboxDestURI\\
Prologue & Application.Prologue.Name & Prologue\\
PrologueArguments & Application.Prologue.Arguments & PrologueArguments\\
Epilogue & Application.Epilogue.Name & Epilogue\\
EpilogueArguments & Application.Epilogue.Arguments & EpilogueArguments\\
AllowZippedISB & Stored internally, not processed & AllowZippedISB\\
ZippedISB & Stored internally, not processed & ZippedISB\\
ExpiryTime & Application.ExpiryTime & ExpiryTime\\
Environment & Application.Environment & Environment\\
PerusalFileEnable & \NST{Stored internally, not processed} & PerusalFileEnable\\
PerusalTimeInterval & \NST{Stored internally, not processed} & PerusalTimeInterval\\
PerusalFilesDestURI & \NST{Stored internally, not processed} & PerusalFilesDestURI\\
InputData \NST{(Deprecated)} & \NM & \NM\\
OutputData \NST{(Deprecated)} & \NM & \NM\\
StorageIndex \NST{(Deprecated)} & \NM & \NM\\
DataCatalog \NST{(Deprecated)} & \NM & \NM\\
DataRequirements & \NST{Stored internally, not processed} & DataRequirements\\
DataAccessProtocol & \NST{Stored internally, not processed} & DataAccessProtocol\\
OutputSE & \NST{Stored internally, not processed} & OutputSE\\
VirtualOrganisation & Identification.JobVOName & VirtualOrganisation\\
RetryCount & Application.Rerun & RetryCount ShallowRetryCount\\
ShallowRetryCount & Application.Rerun & RetryCount ShallowRetryCount\\
LBAddress & \NST{Stored internally, not processed} & LBAddress\\
MyProxyServer & Application.CredentialService & MyProxyServer\\
HLRLocation & \NST{Stored internally, not processed} & HLRLocation\\
JobProvenance & \NST{Stored internally, not processed} & JobProvenance\\
NodeNumber & \NST{Stored internally, not processed} & NodeNumber\\
JobSteps \NST{(Deprecated)} & \NM & \NM\\
CurrentStep \NST{(Deprecated)} & \NM & \NM\\
JobState \NST{(Deprecated)} & \NM & \NM\\
ListenerPort & \NST{Stored internally, not processed} & ListenerPort\\
ListenerHost & \NST{Stored internally, not processed} & ListenerHost\\
ListenerPipeName & \NST{Stored internally, not processed} & ListenerPipeName\\
Requirements & \NST{Stored internally, not processed} & Requirements\\
Rank & JobMeta.Rank & Rank\\
FuzzyRank & JobMeta.FuzzyRank & FuzzyRank\\
UserTags & Identification.UserTag & UserTags\\
BatchSystem & \NST{Stored internally, not processed} & BatchSystem\\
QueueName & Resources.CandidateTarget.QueueName & QueueName
\end{tabularx}
\end{center}
